Endogenous long-run output impacts of monetary and fiscal policy: a growth theory approach

### 2021-12-04 paper.tex
added variable in document

\subsection{Steady state}
If \(\gamma_0+\gamma_1 (i^*-i)+\gamma_2 g <0\) then \(L_2(t)\) will shrink to zero and \(A(t)\) will converge to a constant.  If \(L_1(t)\) continues to grow (is not crowded out by \(L_3(t)\)), the economy reaches a long-run steady state in much the same way as the traditional Solow model.

\subsection{Economic collapse}
If either \(L_2\) or \(L_3\) grow too large, either \(K\) or \(L_1\) can shrink to zero.  This can occur if interest rates are held too low or \(g\) is too large.  \(L_2\) will grow too quickly if \(\gamma_0+\gamma_1 (i^*-i)+\gamma_2 g > \eta\).  Likewise, \(L_3\) will crowd out \(L_1\) if \(v_0+v_1g > \eta\) and \(g\) IS SOMETHING.

@@

Since the model is a system of non-linear differential equations, the model must be solved numerically.  I show plots of two economies under different interest rate and fiscal policy regimes.

>>>>

\subsubsection{Steady state}
If \(\gamma_0+\gamma_1 (i^*-i)+\gamma_2 g <0\) then \(L_2(t)\) will shrink to zero and \(A(t)\) will converge to a constant.  If \(L_1(t)\) continues to grow (is not crowded out by \(L_3(t)\)), the economy reaches a long-run steady state in much the same way as the traditional Solow model.

\subsubsection{Economic collapse}
If either \(L_2\) or \(L_3\) grow too large, either \(K\) or \(L_1\) can shrink to zero.  This can occur if interest rates are held too low or \(g\) is too large.  \(L_2\) will grow too quickly if \(\gamma_0+\gamma_1 (i^*-i)+\gamma_2 g > \eta\).  Likewise, \(L_3\) will crowd out \(L_1\) if \(v_0+v_1g > \eta\) and \(g\) IS SOMETHING.

@@

Since the model is a system of non-linear differential equations, the model must be solved numerically.  I show plots of two economies under different interest rate and fiscal policy regimes.  The full parameters for these two economies:

\begin{center}
\begin{tabular}{ c c c }
      Variable  & Economy 1 Value & Economy 2 Value \\ 
      \(\eta\) & 0.02 & 0.02 \\  
      \(\gamma_0\) & 0.004 & 0.04  \\  
      \(\gamma_1\) & 0.2 & 0.2  \\  
      \(\gamma_2\) & 0.005 & 0.005  \\ 
      \(v_0\) & 0.001 & 0.001  \\  
      \(v_1\) & 0.05 & 0.05  \\  
      \(\beta\) & 0.03 & 0.03  \\  
      \(\alpha\) & 0.4 & 0.4  \\  
      \(\delta\) & 0.1 & 0.1  \\  
      \(s\) & 0.3 & 0.3  \\ 
      \(L_1(0)\) & 3.0 & 3.0  \\ 
      \(L_2(0)\) & 1.0 & 1.0  \\ 
      \(L_3(0)\) & 1.0 & 1.0  \\ 
      \(A(0)\) & 2.0 & 2.0  \\ 
      \(K(0)\) & 10.0 & 10.0  
\end{tabular}
\end{center}
